\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliography}
\bibitem{digiconomist}Bitcoin Energy Consumption Index, \url{https://digiconomist.net/bitcoin-energy-consumption}, 10th of November 2017, accessed 10th of November 2017.

\bibitem{bitcoin_mining_pools} Jordan Tuwiner: Bitcoin Mining Pools, \url{https://www.buybitcoinworldwide.com/mining/pools/}, 13th of July 2017, accessed 30th of December 2017.

\bibitem{bitcoin_mining_pools_2} Hashrate Distribution, \url{https://blockchain.info/pools?timespan=4days}, 30th of December 2017, accessed 30th of December 2017.

\bibitem{51_attack} Daniel Cawrey: Are 51\% Attacks a Real Threat to Bitcoin?, \url{https://www.coindesk.com/51-attacks-real-threat-bitcoin/}, 20th of June 1014, accessed 30th of December 2017.

\bibitem{bitcoin_cloud_mining} Jordan Tuwiner: Bitcoin Cloud Mining, \url{https://www.buybitcoinworldwide.com/mining/cloud-mining/}, 13th of June 2017, accessed 30th of December 2017.

\bibitem{tendermit_paper} Jae Kwon: Tendermint: Consensus without Mining, \url{https://tendermint.com/static/docs/tendermint.pdf}, 2014, accessed 10th of November 2017.

\bibitem{ethereum_faq} Vitalik Buterin: Proof of Stake FAQ, \url{https://github.com/ethereum/wiki/wiki/Proof-of-Stake-FAQ},  1st of November 2017, accessed 10th of November 2017.

\bibitem{tendermit_docs} Tendermint Documentation, \url{http://tendermint.readthedocs.io/projects/tools/en/master/introduction.html},  2017, accessed 10th of November 2017.

\bibitem{algorand_paper} Yossi Gilad, Rotem Hemo, Silvio Micali, Georgios Vlachos, Nickolai Zeldovich: Algorand: Scaling Byzantine Agreements for Cryptocurrencies, \url{https://people.csail.mit.edu/nickolai/papers/gilad-algorand-eprint.pdf} accessed 10th of November 2017.

\bibitem{cryptocurrencies-without-pow} Iddo Bentov, Ariel Gabizon, Alex Mizrahi: Cryptocurrencies without Proof of Work, \url{https://bravenewcoin.com/assets/Whitepapers/Cryptocurrencies-without-Proof-of-Work.pdf}, accessed 10th of November 2017.

\bibitem{ppcoin_paper} Sunny King, Scott Nadal: PPCoin: Peer-to-Peer Crypto-Currency with Proof-of-Stake, \url{https://peercoin.net/assets/paper/peercoin-paper.pdf}, 19th of August 2012, accessed 10th of November 2017.

\bibitem{bazo_paper} Livio Sgier: Bazo - A Cryptocurrency from Scratch, 23rd of August 2017, accessed 10th of November 2017.

\bibitem{antminer-s9} Jordan Tuwiner: Bitmain Antminer S9 Review, \url{https://www.buybitcoinworldwide.com/mining/hardware/antminer-s9/}, 27th of June 2017, accessed 30th of December 2017.

\end{thebibliography}

